XS-Face: Merge Raw Data

### 2020-04-10 writeup-paper/old-drafts/step1_merge_data.Rmd
add writeup folder for apa draft

```{r}
detsOpenPose <- read_csv("../data/final_detector_output/openpose_results_truncated_2.csv") 
detsOpenPose <- detsOpenPose %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  mutate(frame = as.numeric(frame) + 1) %>% ## Frame output is off by one since we extracted from videos vs. frames.
  mutate(faceOP = Nose_conf!=0)  %>%  
  mutate(wristOP = LWrist_conf!=0 | RWrist_conf!=0 )   
```

@@

### Complete the data frame 
So that zeros get counted: expands so that each subid includes a zero length row for each posture and orientation.
This was annoying.
```{r}
ages <- d %>%
  group_by(subid) %>%
  summarise(age.grp = mean(age.grp))

>>>>

```{r}
detsOpenPose <- read_csv("../data/final_detector_output/openpose_results_truncated_2.csv") 
detsOpenPose <- detsOpenPose %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  mutate(frame = as.numeric(frame) + 1) %>% ## Frame output is off by one since we extracted from videos vs. frames.
  mutate(faceOP = Nose_conf!=0)  %>%  
  mutate(wristOP = LWrist_conf!=0 | RWrist_conf!=0 )%>%
  mutate(armOP = LElbow_conf!=0 | RElbow_conf!=0)
```

@@

### Complete the data frame 
So that zeros get counted: expands so that each subid includes a zero length row for each posture and orientation.
This was annoying.
```{r}
ages <- d %>%
  group_by(subid) %>%
  summarise(age.grp = age.grp[1], age.at.test = age.at.test[1])  ## added age.at.test
